\bfseries \boldmath \scititle

### 2025-12-20 latex/main.tex
Partial updates to move Methods to supplement

\date{}

% \author[1,2,8,*,\orcidlink{0000-0002-6351-8873}]{Shing~H.~Zhan}
% \author[1,7,\orcidlink{0000-0002-3536-6411}]{Yan~Wong}
% \author[3,7,\orcidlink{0000-0001-6402-9396}]{Anastasia~Ignatieva}
% \author[4,\orcidlink{0000-0001-6862-7756}]{Katherine~Eaton}
% \author[1,\orcidlink{0000-0002-3547-7226}]{Isobel~Guthrie}
% \author[1,\orcidlink{0000-0002-1982-6801}]{Benjamin~Jeffery}
% \author[1,3,5,\orcidlink{0000-0002-0824-0047}]{Duncan~S.~Palmer}
% \author[4,\orcidlink{0000-0002-1543-4501}]{Carmen~Lia~Murall}
% \author[6,\orcidlink{0000-0003-3042-0818}]{Sarah~P.~Otto}
% \author[1,**,\orcidlink{0000-0002-7894-5253}]{Jerome~Kelleher}

@@

% \affil[*]{Correspondence: shing.zhan@ndph.ox.ac.uk}
% \affil[**]{Correspondence: jerome.kelleher@bdi.ox.ac.uk}

\begin{document}
\maketitle

@@

\section*{RESULTS}

%%% The results may be divided with subheadings.
%%% In our view, good subheadings convey information about the findings,
%%% so we encourage you to be specific. For example, "Factor X requires factor Y to function in process Z"
%%% is better than "Analysis of factors X and Y by approach Q."
%%% We recommend that you use similar language in your figure titles for clarity and structural harmony.
%%% Please do not use numbered subheadings. For some formats, ``results and discussion" may be combined under a single heading.

%%% For initial submissions, figures and their titles and legends can be run-in with the text.
%%% For final submissions, the image files must be uploaded as separate files, one complete file per figure. The figure titles and legends should be placed toward the end of the main text, after the declaration of interests. Our typesetters will place the figures and their titles and legends appropriately based on your in-text citations.

%%% To cite/link to display items (figures and tables) and/or sections of the manuscript,
%%% simply write, for example, ``(Figure 1)" or ``see discussion."
%%% Our team will do the rest. Please note that we do not number sections or subsections.

@@

\section*{STAR METHODS}

%%%  The STAR Methods should appear in your main
%%%  manuscript file after the figure legends, main
%%%  table(s) and table legend(s).

% \subsection*{Key resources table}

% \textit{To create the KRT, please use the \href{https://star-methods.com}{KRT webform} or the \href{http://www.cell.com/pb-assets/journals/research/cell/methods/table-template1.docx}{Word template} and upload this file separately.}

\subsection*{Method details}

%%%  Please provide precise details of all the
%%%  procedures in the paper (behavioral task,
%%%  generation of reagents, biological assays,
%%%  modeling, etc.) such that it is clear how,
%%%  when, where, and why procedures were
%%%  performed. We encourage authors to provide
%%%  information related to the experimental
%%%  design as suggested by NIH and ARRIVE
%%%  guidelines (e.g., information about
%%%  replicates, randomization, blinding, sample
%%%  size estimation, and the criteria for
%%%  inclusion and exclusion of any data or
%%%  subjects).

>>>>

% \author[1,2,8,*]{Shing~H.~Zhan}
% \author[1,7]{Yan~Wong}
% \author[3,7]{Anastasia~Ignatieva}
% \author[4]{Katherine~Eaton}
% \author[1]{Isobel~Guthrie}
% \author[1]{Benjamin~Jeffery}
% \author[1,3,5]{Duncan~S.~Palmer}
% \author[4]{Carmen~Lia~Murall}
% \author[6]{Sarah~P.~Otto}
% \author[1,**]{Jerome~Kelleher}

@@

% \affil[*]{Correspondence: shing.zhan@ndph.ox.ac.uk}
% \affil[**]{Correspondence: jerome.kelleher@bdi.ox.ac.uk}
\begin{document}

\maketitle

@@

% Research Articles and Reviews split the text into sections using headings

@@

\begin{center}
\section*{Supplementary Materials for\\ \scititle}

% Author list for the supplement
% Indicate the corresponding authors, but do NOT include institutions here
% It would be nice if the template auto-generated this, but doing so is complicated...
First~Author$^{\ast\dagger}$,
A.~Scientist$^\dagger$,
Someone~E.~Else\\ % we're not in a \author{} environment this time, so use \\ for a new line
\small$^\ast$Corresponding author. Email: example@mail.com\\
\small$^\dagger$These authors contributed equally to this work.
\end{center}

% Fill out the numbers for each type of supplementary material,
% and delete any lines that aren't applicable.
% These are just example numbers that don't match the rest of this template.
\subsubsection*{This PDF file includes:}
Materials and Methods\\
Supplementary Text\\
Figures S1 to S3\\
Tables S1 to S4\\
Captions for Movies S1 to S2\\
Captions for Data S1 to S2

\subsubsection*{Other Supplementary Materials for this manuscript:}
Movies S1 to S2\\
Data S1 to S2

\subsection*{Materials and Methods}
